Review stages

### 2024-06-06 doc/review-stages.qmd
docs: added code chunk to show number of kept abstracts

```{r}
#| message: false
```

@@

>>>>

@@

The second phase of the review is looking over the abstracts. In
@tbl-abstracts-kept below are the number of articles each reviewer kept
after this second screening.

```{r tbl-abstracts-kept}
#| message: false
#| tbl-cap: "Number of articles each reviewer kept after the second screening of the abstracts."
targets::tar_read(abstracts_kept) |> 
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()

# targets::tar_read(abstracts_kept) |> 
#   select("Article titles" = title) |>
#   knitr::kable()
```
